ms2

### 2017-09-25 ms2/ms2_display.Rmd
improved lm summaries

# Use the zipcode-HRR mapping from 2011
hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  filter(year==2011) %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

@@

state_abg = read_tsv('abg_state.tsv')
hrr_abg = read_tsv('abg_hrr.tsv')
```

@@

```{r fnz_mup_by_drug}
ineq %>%
  filter(unit_type=='hrr') %>%
  #rename(state=unit) %>% left_join(regions, by='state') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_regions) %>%
  ggplot(aes(x=fnz, y=mup, color=region)) +
  facet_wrap(~drug_group, scales='free') +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='gray') +
  geom_smooth(method='lm', se=F) +
  geom_point(shape=1) +
  xlab(expression(f['>'])) +
  ylab(expression(mu['>'])) +
  ggtitle('Mean nonzero consumption vs. fraction consuming, states') +
  theme_minimal()
```

@@

```{r ecoli_bactrim_fnz_hrr}
ineq %>%
  filter(unit_type=='hrr') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(mean_percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=fnz, y=mean_percent_nonsusceptible, color=region)) +
  geom_abline(intercept=16.86, slope=114.8, color='pink') +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed Bactrim') +
  ylab('Bactrim-resistance E. coli') +
  ggtitle('E. coli & Bactrim across HRRs')
```

@@

```{r ecoli_bactrim_fnz_state}
ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  ggplot(aes(x=fnz, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed Bactrim') +
  ylab('Bactrim resistance E. coli') +
  ggtitle('E. coli & Bactrim across states')
```

@@

```{r ecoli_bactrim_mup}
ineq %>%
  filter(unit_type=='hrr') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(mean_percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('mean Bactrim cons. among Bactrim-eaters') +
  ylab('Bactrim-resistance E. coli') +
  ggtitle('E. coli & Bactrim, mu>, HRRs')
```

@@

```{r efaecium_betalactam}
ineq %>%
  filter(unit_type=='hrr') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='Ec. faecium', drug_group=='beta_lactam') %>%
  ggplot(aes(x=fnz, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance in E. faecium') +
  ggtitle('E. faecium & beta-lactams across HRRs')

ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='Ec. faecium', drug_group=='beta_lactam') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance E. coli') +
  ggtitle('E. faecium & beta-lactams across states')
```

@@

```{r pneumo_tetra}
ineq %>%
  filter(unit_type=='hrr') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='S. pneumoniae', drug_group=='tetracycline') %>%
  ggplot(aes(x=fnz, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed tetra') +
  ylab('tetra resistance pneumo') +
  ggtitle('pneumo & tetra across HRRs')

ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='S. pneumoniae', drug_group=='tetracycline') %>%
  ggplot(aes(x=fnz, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed tetra') +
  ylab('tetra resistance pneumo') +
  ggtitle('pneumo & tetra across states')
```

@@

```{r ecoli_betalactam}
ineq %>%
  filter(unit_type=='hrr') %>%
  mutate(hrr=as.integer(unit)) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='beta_lactam') %>%
  filter(mean_percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=fnz, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance in E. coli') +
  ggtitle('E. coli & beta-lactams across HRRs')

ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='beta_lactam') %>%
  filter(mean_percent_nonsusceptible < 50) %>% # filter one crazy point
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance E. coli') +
  ggtitle('E. coli & beta-lactams across states')
```

@@

```{r ecoli_quin_state}
state_cons_res_plot = function(b, d) {
  p = inner_join(
    ineq %>%
      filter(unit_type=='state', drug_group==d) %>%
      select(state=unit, mean),
    state_abg %>%
      filter(bug==b, drug_group==d) %>%
      select(state, mean_percent_nonsusceptible),
    by='state') %>%
    left_join(regions, by='state') %>%
    ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state, color=region)) +
    geom_smooth(method='lm', se=F) +
    geom_smooth(method='lm', se=F, col='gray') +
    geom_point() +
    geom_text() +
    xlab(str_interp('mean ${d} claims per beneficiary')) +
    ylab(str_interp('mean percent nonsusceptible ${b} isolates')) +
    ggtitle(str_interp('${b} & ${d}, state'))

>>>>

# Use the zipcode-HRR mapping from 2011
hrr = read_tsv('../../db/hrr/hrr.tsv', col_types=list(hrr='c')) %>%
  filter(year==2011) %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

@@

state_abg = read_tsv('abg_state.tsv')
hrr_abg = read_tsv('abg_hrr.tsv', col_types=list(hrr='c'))
```

@@

```{r fnz_mup_by_drug}
ineq %>%
  filter(unit_type=='hrr') %>%
  #rename(state=unit) %>% left_join(regions, by='state') %>%
  rename(hrr=unit) %>% left_join(hrr_regions, by='hrr') %>%
  ggplot(aes(x=fnz, y=mup, color=region)) +
  facet_wrap(~drug_group, scales='free') +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='gray') +
  geom_smooth(method='lm', se=F) +
  geom_point(shape=1) +
  xlab(expression(f['>'])) +
  ylab(expression(mu['>'])) +
  ggtitle('Mean nonzero consumption vs. fraction consuming, states') +
  theme_minimal()
```

@@

```{r ecoli_bactrim_fnz_hrr}
ineq %>%
  filter(unit_type=='hrr') %>%
  rename(hrr=unit) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=fnz, y=percent_nonsusceptible, color=region)) +
  geom_abline(intercept=16.86, slope=114.8, color='pink') +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed Bactrim') +
  ylab('Bactrim-resistance E. coli') +
  ggtitle('E. coli & Bactrim across HRRs')
```

@@

```{r ecoli_bactrim_fnz_state}
ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  ggplot(aes(x=fnz, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed Bactrim') +
  ylab('Bactrim resistance E. coli') +
  ggtitle('E. coli & Bactrim across states')
```

@@

```{r ecoli_bactrim_mup}
ineq %>%
  filter(unit_type=='hrr') %>%
  rename(hrr=unit) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=mean, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('mean Bactrim cons. among Bactrim-eaters') +
  ylab('Bactrim-resistance E. coli') +
  ggtitle('E. coli & Bactrim, mu>, HRRs')
```

@@

```{r efaecium_betalactam}
ineq %>%
  filter(unit_type=='hrr') %>%
  rename(hrr=unit) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='Ec. faecium', drug_group=='beta_lactam') %>%
  ggplot(aes(x=fnz, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance in E. faecium') +
  ggtitle('E. faecium & beta-lactams across HRRs')

ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='Ec. faecium', drug_group=='beta_lactam') %>%
  ggplot(aes(x=mean, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance E. coli') +
  ggtitle('E. faecium & beta-lactams across states')
```

@@

```{r pneumo_tetra}
ineq %>%
  filter(unit_type=='hrr') %>%
  rename(hrr=unit) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='S. pneumoniae', drug_group=='tetracycline') %>%
  ggplot(aes(x=fnz, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed tetra') +
  ylab('tetra resistance pneumo') +
  ggtitle('pneumo & tetra across HRRs')

ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='S. pneumoniae', drug_group=='tetracycline') %>%
  ggplot(aes(x=fnz, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed tetra') +
  ylab('tetra resistance pneumo') +
  ggtitle('pneumo & tetra across states')
```

@@

```{r ecoli_betalactam}
ineq %>%
  filter(unit_type=='hrr') %>%
  rename(hrr=unit) %>% left_join(hrr_regions, by='hrr') %>%
  right_join(hrr_abg, by=c('hrr', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='beta_lactam') %>%
  filter(percent_nonsusceptible < 50) %>% # filter one crazy Nevada point
  ggplot(aes(x=fnz, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance in E. coli') +
  ggtitle('E. coli & beta-lactams across HRRs')

ineq %>%
  filter(unit_type=='state') %>%
  rename(state=unit) %>%
  left_join(regions, by='state') %>%
  right_join(state_abg, by=c('state', 'drug_group')) %>%
  filter(bug=='E. coli', drug_group=='beta_lactam') %>%
  filter(percent_nonsusceptible < 50) %>% # filter one crazy point
  ggplot(aes(x=mean, y=percent_nonsusceptible, color=region)) +
  geom_smooth(method='lm', se=F, aes(color=NULL), color='black') +
  geom_smooth(method='lm', se=F) +
  geom_point() +
  xlab('fraction who consumed beta-lactams') +
  ylab('Beta-lactam resistance E. coli') +
  ggtitle('E. coli & beta-lactams across states')
```

@@

```{r ecoli_quin_state}
state_cons_res_plot = function(b, d) {
  p = inner_join(
    ineq %>%
      filter(unit_type=='state', drug_group==d) %>%
      select(state=unit, mean),
    state_abg %>%
      filter(bug==b, drug_group==d) %>%
      select(state, percent_nonsusceptible),
    by='state') %>%
    left_join(regions, by='state') %>%
    ggplot(aes(x=mean, y=percent_nonsusceptible, label=state, color=region)) +
    geom_smooth(method='lm', se=F) +
    geom_smooth(method='lm', se=F, col='gray') +
    geom_point() +
    geom_text() +
    xlab(str_interp('mean ${d} claims per beneficiary')) +
    ylab(str_interp('mean percent nonsusceptible ${b} isolates')) +
    ggtitle(str_interp('${b} & ${d}, state'))
